Illustration of Adaptive Shrinkage

### 2016-09-29 analysis/adaptive_shrinkage.Rmd
Working through adaptive_shrinkage.Rmd.

```{r chunk-options, include=FALSE}
source("chunk-options.R")
```

@@

We simulate from two scenarios, the first with effects more peaked about zero, the second with effects less peaked.
```{r initialize}
set.seed(100)
library(ashr)
library(ggplot2)
library(scales)
#load the simulation function, (rnormmix_datamaker)
source("../code/dsc-shrink/datamakers/datamaker.R")

>>>>

@@

TO DO: explain what this chunk does.

```{r chunk-options,include = FALSE}
source("chunk-options.R")
```

We simulate from two scenarios, the first with effects more peaked
about zero, the second with effects less peaked.

```{r initialize}
set.seed(100)
library(ashr)
library(ggplot2)
library(scales)
source("../code/dsc-shrink/datamakers/datamaker.R")
